---
title: "BRIDGE Cost"
author: "Astrid"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---

Source: Local collection
Currency: Originially Naira, Need to be converted into USD based on the 2023 exchange rate: 540.8564

https://www.exchangerates.org.uk/USD-NGN-spot-exchange-rates-history-2023.html

Because we're estimate the present-day policy, all the unit cost will be based on the 2023 version(which is the MAX in the excel sheet). 

```{r parameterization_unit_cost}
cVisit_CHW_2023 = 500
cVisit_Physician_Private_2023 = 5000
cVisit_Physician_Gov_2023 = 2000
cSupervision_CHW_2023 = 1000

cAdmission_Hosp_Private_2023 = 10000
cAdmission_Hosp_Gov_2023 = 3000
cMRI_scan_2023 = 70000
cEEG_2023 = 20
cCT_scan_2023 = 40000

cPhenobarbitone_2023 = 24
cCarbamazepine_2023 = 16
cValproate_2023 = 62
cPhenytoin_2023 = 68
cLevetracetam_2023 = 83
cGabapentin_2023 = 70
# cLamotrigine

cCatering_2023 = 3000
cTraining_Facilitator_2023 = 1000
cTraining_CHW_2023 = 500
cTraining_Admin_2023 = 1000
cTravel_Facilitator_2023 = 40
cTravel_CHW_2023 = 40

exchange_Naira_to_USD = 1/540.8564
```

It is hard to track any individual's changes, I feel the CEA per individual is hard to estimate.
I'm able to get the total DALY for all patients in this project(after 2 years, they have an improvement -- maybe not exactly 2 year but we can calculate from the beginning to the end), and I'm able to get all consumed units in this project. 

There maybe some dropout in the research, it is like the waste and will be kept in the cost calculation. 

```{r treatment length}
fudw
```

```{r unit_count}
# Year 1: between 7/1/2020 - 6/30/2021
nVisit_CHW_Year1 = 4505
nVisit_Physician_Private_2023 = 5000
cVisit_Physician_Gov_2023 = 2000
cSupervision_CHW_2023 = 1000

cAdmission_Hosp_Private_2023 = 10000
cAdmission_Hosp_Gov_2023 = 3000
cMRI_scan_2023 = 70000
cEEG_2023 = 20
cCT_scan_2023 = 40000

cPhenobarbitone_2023 = 24
cCarbamazepine_2023 = 16
cValproate_2023 = 62
cPhenytoin_2023 = 68
cLevetracetam_2023 = 83
cGabapentin_2023 = 70
# cLamotrigine

cCatering_2023 = 3000
cTraining_Facilitator_2023 = 1000
cTraining_CHW_2023 = 500
cTraining_Admin_2023 = 1000
cTravel_Facilitator_2023 = 40
cTravel_CHW_2023 = 40


# Year 2: between 7/1/2021 - 6/30/2022




# Year 3: between 7/1/2022 - 6/30/2023






```

Use two arms' sum costs's difference to calculate!!