---
title: "Detailed DALY & Cycle Check"
author: "Astrid Yu, Ashley Leech"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
library(tidyverse)
```



### intervals

**Expected schedule of follow-up visits** Only the first follow-up needs to be +/- 3 days, all else allow +/- 14 days.\
*Schedule:*\
\* instance 1 - Week 1\
\* instance 2 - Month 1\
\* instance 3 - Month 2\
\* instance 4 - Month 4\
\* instance 5 - Month 6\
\* instance 6 - Month 9\
\* instance 7 - Month 12\
\* instance 8 - Month 15\
\* instance 9 - Month 18\
\* instance 10 - Month 24\
*Expected time interval:*\
\* v1: 7 +/- 3 from v0\
\* v2: 28 +/- 14 from v0\
\* v3: 28 +/- 14 from v2\
\* v4: 56 +/- 14 from v3\
\* v5: 56 +/- 14 from v4\
\* v6: 84 +/- 14 from v5\
\* v7: 84 +/- 14 from v6\
\* v8: 84 +/- 14 from v7\
\* v9: 84 +/- 14 from v8\
\* v10: 168 +/- 14 from v9

**549 / 1792**

```{r elig-fu}
fudw %>% filter(date_1 > date_0 + 10 | date_1 < date_0 + 4)
fudw %>% filter(date_2 > date_0 + 42 | date_2 < date_0 + 14)
fudw %>% filter(date_3 > date_2 + 42 | date_3 < date_2 + 14)
fudw %>% filter(date_4 > date_3 + 70 | date_4 < date_3 + 42)
fudw %>% filter(date_5 > date_4 + 70 | date_5 < date_4 + 42)
fudw %>% filter(date_6 > date_5 + 98 | date_6 < date_5 + 70)
fudw %>% filter(date_7 > date_6 + 98 | date_7 < date_6 + 70)
fudw %>% filter(date_8 > date_7 + 98 | date_8 < date_7 + 70)
fudw %>% filter(date_9 > date_8 + 98 | date_9 < date_8 + 70)
fudw %>% filter(date_10 > date_9 + 182 | date_10 < date_9 + 154)

fudw %>% filter(date_1 > date_0 + 10 | date_1 < date_0 + 4 | date_2 > date_0 + 42 | date_2 < date_0 + 14 | date_3 > date_2 + 42 | date_3 < date_2 + 14 | date_4 > date_3 + 70 | date_4 < date_3 + 42 | date_5 > date_4 + 70 | date_5 < date_4 + 42 | date_6 > date_5 + 98 | date_6 < date_5 + 70 | date_7 > date_6 + 98 | date_7 < date_6 + 70 | date_8 > date_7 + 98 | date_8 < date_7 + 70 | date_9 > date_8 + 98 | date_9 < date_8 + 70 | date_10 > date_9 + 182 | date_10 < date_9 + 154)

```